Nail: A practical interface generator for data formats

### 2014-04-24 paper/osdi14/design.tex
Some paper changes

@@

\paragraph{Fundamental parsers.}
The elementary parsers of Nail are the same as those of Hammer, signed
and unsigned integers with arbitrary lengths up to 64 bits.  Note that is
possible to define parsers for sub-byte lengths, e.g. to parse the 4-bit
data offset within the TCP header; in Nail's syntax.  Integer parsers
return their value in the smallest appropriately sized machine integer
type; e.g., a 24-bit integer is stored in a 32-bit wide variable.

>>>>

Nail grammars describe not only a

@@

\paragraph{Integers and Constraints}
Nail's fundamental 
The elementary parsers of Nail are the same as those of Hammer, signed
and unsigned integers with arbitrary lengths up to 64 bits.  Note that is
possible to define parsers for sub-byte lengths, e.g. to parse the 4-bit
data offset within the TCP header; in Nail's syntax.  Integer parsers
return their value in the smallest appropriately sized machine integer
type; e.g., a 24-bit integer is stored in a 32-bit wide variable.

### 2014-04-24 paper/osdi14/eval.tex
Some paper changes

\section{Evaluation}
\label{s:eval}

\input{fig-dnsfull}

In our preliminary evaluation of Nail, we try to answer two questions:

\begin{itemize}
\item Can Nail grammars support real-world data formats?
\item How much programmer effort is required to build an
      application that uses Nail for data input and output?
\end{itemize}

\paragraph{Data formats.}

To answer the first question, we implemented two Nail grammars:
one for UTF-16 encoded strings, exposing an array of code points
(shown in Figure~\ref{fig:utf16}), and another for a subset of DNS
packets sent to and from an authoritative name server, without label
compression, as per RFC1035 (shown in Figure~\ref{fig:dns-full}).
Furthermore, our GitHub repository contains other Nail
grammars, such as a TAP network stack that processes Ethernet,
ARP, ICMP, IP, and UDP packets, and the grammar for Nail
itself.\footnote{\url{https://github.com/jbangert/nail/tree/master/examples}}
The results suggest that Nail is a good fit for these data formats.

\paragraph{Programmer effort.}

To answer the second question, we implemented a functioning toy DNS
server.  In particular, we cloned the test DNS server from the Hammer
distribution to Nail.  Hammer ships with a toy DNS server written in 683
lines of code, excluding the Hammer framework itself, that responds to
any valid DNS query with a CNAME record to the domain ``spargelze.it''.
Most of this code is taken up with custom validators, semantic actions,
and data structure definitions, with only 52 lines of code defining the
grammar with Hammer's combinators.

@@

>>>>

\section{Evaluation}
\label{s:eval}
\input{fig-ethernet}
\input{fig-dnsfull}
\input{fig-zip}
In our preliminary evaluation of Nail, we try to answer four questions:

\begin{itemize}
\item Can Nail grammars support real-world data formats?
\item How much programmer effort is required to build an
      application that uses Nail for data input and output?
\item Do applications handling input and output with Nail suffer from less security vulnerabilities?
\item How fast are systems using Nail parsers as opposed to hand-written input handling? 
\end{itemize}

\subsection{Data formats.}
\label{s:eval-formats}
To answer the first question, we implemented grammars for four protocols with particularly
challenging features and show that Nail is a good fit for these data formats. In
\S\ref{s:eval-effort} we will demonstrate that Nail is easier to use than hand-written parsers and
more convenient than state-of-the-art parser generators for formats that they can handle.

In particular, we show extracts from grammars for the following protocols: 
\begin{itemize}
\item A subset of Ethernet network packets, containing ARP, ICMP and UDP/IP packets. See Figure~\ref{fig:ethernet-extract}.
\item DNS packets as described in RFC 1035, featuring label compression. See Figure~\ref{fig:dns-full}.
\item ZIP files, with compression, check-sums and a complicated procedure to identify the header.
  See Figure~\ref{fig:zip-extract}.
\end{itemize}

one for  DNS queries and respones, as per RFC1035 (shown in, one for the ZIP
archive format and a grammar for Ethernet frames containing ARP, ICMP and UDP packets. We also
parse Nail grammars with Nail, demonstrating that our system can also handle text-based protocols
and languages.

The results suggest that Nail is a good fit for these data formats.

\subsection{Programmer effort.}
\label{s:eval-effort}
To answer the second question, we implemented small example applications based on the above
grammars and compared code size with comparable applications written without parser generators. We
also compare our DNS implementation to the example DNS application provided with the Hammer parser generator.

 a functioning toy DNS
server.  In particular, we cloned the test DNS server from the Hammer
distribution to Nail.  Hammer ships with a toy DNS server written in 683
lines of code, excluding the Hammer framework itself, that responds to
any valid DNS query with a CNAME record to the domain ``spargelze.it''.
Most of this code is taken up with custom validators, semantic actions,
and data structure definitions, with only 52 lines of code defining the
grammar with Hammer's combinators.

@@

\paragraph{Security}
